\def\rank{\mathop{\rm rank}}
\def\wgt{\mathop{\rm wgt}}
\def\lc{\mathop{\rm lc}}
\def\ker{\mathop{\rm Ker}}
\def\im{\mathop{\rm Im}}
\documentclass[aps,%prb,12pt,tightenlines,%
pra, twocolumn,%superscriptaddress,%
%galley,
notitlepage,longbibliography]{revtex4-2}
%\advance\textheight by -5.2in
%\advance\textheight by -2.25in
\usepackage{hyperref}
\usepackage{amsmath}
%\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{array}
%\usepackage{enumitem}
%\usepackage{datetime}
\newtheorem{theorem}{Theorem}
\newtheorem{example}[theorem]{Example}
\newtheorem{note}[theorem]{Note}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\begin{document}
\title{On random window algorithm}
\date\today
\date{\today\ \bf \jobname} 
%\date{\today\ \currenttime\ \bf \jobname} 
\author{Weilei Zeng}
\affiliation{Department of Physics \& Astronomy, University of California,
  Riverside, California 92521, USA}
\email{wzeng002@ucr.edu}

\begin{abstract}
  note on random window decoder  
\end{abstract}
\maketitle

\tableofcontents


\section{introduction}
The random window algorithm can be used to quickly estimate an upper
bound of the distance of an error correcting code. In most cases, the
upper bound matches its actual distance. It was invented and named information
set algorithm in \cite{prange1962use, chua1988cellular} and explained
as covering set
algorithm in \cite{dumer2017distance}.

Because a decoder return the closest codeword upon given input, it can
also be used to esitimate the distance.


\section{distance of a binary CSS code}

input: stabilizer generator $G_X$, $G_Z$ with $G_XG_Z^T=0$

solve for codeword generating matrix $C_Z$ such that $G_XC_Z^T=0$,
$\rank(G_X) +\rank(G_Z) + \rank(C_Z) =0$ and $C_Z$ is independet from
$G_Z$. This is done by first solve for dual matrix $G_XQ_Z^T=0$, then
use gaussian ellemination to remove the dependent rows in $Q_Z$.

* do a gaussian elimination of $C_Z$ and pick the row with min weight.

do a random column permutation on $C_Z$

go back to step * and repeat certain amount of times, record the min
weight, which is an upper bound of Z distance.

do the same thing to get X distance.



\section{estimate distance of a classical binary code}

input: binary code $GH^T=0$ with codeword generating matrix $G$ and
parity check matrix $H$

* use gaussian elimination to transform $G$ into row reduce echelon form

get min row weight and update to distance if smaller.

do a column permutation ( or a row permutation ) and repeat * certain
amount of time.

return min distance as an upper bound of the distance.




\section{decode a non-CSS quantum code}


Gauge generator matrix $G=(G_X|G_Z)$, $\tilde{G}=(G_Z|G_X)$\\
$\tilde{G}S^T=0 \longrightarrow \text{ stabilzier generator matrix: }  S=(S_X|S_Z)$\\
input error: $\tilde{e}=(e_Z|e_X)$\\
syndrome $ s^T=S\tilde{e}^T=$
modified parity check matrix: $H=(S_X|S_Z|s)$\\
solve for dual matrix: $HQ^T=0 \longrightarrow  Q=(Q_Z|Q_X|1)$
last row of Q gives the error detected $\tilde{e'}=(e_Z|e_X)$ with an extra 1 in the end.\\
Difference $\tilde{d}=\tilde{e}+\tilde{e'}$\\

Check if $d$ is a codeword or trial cycle.

$\tilde C  d^T = 0$ means it is trial

$\tilde C  d^T \neq 0$ means it is a codeword

add $\tilde{d}$ to $G$ as an extra row and check the rank of $G'$\\
If not full rank: $\tilde{d} \subset \tilde{G} \longrightarrow $ good error\\ 
If full rank:     $\tilde{d} \not\subset \tilde{G} \longrightarrow $ bad error\\ 





\bibliography{WeileiBibFile}
%\bibliography{lpp,qc_all,more_qc,ldpc,linalg,percol,sg}
\end{document}
